flowers-pilot-analysis

### 2021-08-19 code/aa-flowers-pilot_analysis.Rmd
add pilot data

# Pre-process
Remove joined_data and uncomment the following block to rerun the preprocessing scripts
```{r process-data, message=FALSE, warning=FALSE}
# data_list <- c("technical_pilots", "collabmulti_pilot0",
#                "collabmulti_20", "compet_20", "multi_nonlang_20")
# process_all_data(data_list)
# join_all_data()
```

@@

```{r}
#exclude BLOCKS with <12 completed (all 3 participants responded) rounds
#exclude trial runs
# exclude 
rounds_exclude <- d.rounds %>% group_by(gameId, blockNum) %>% tally() %>% filter(n!=36) %>% select(gameId,blockNum)

@@

d.raw_chat.final <- d.raw_chat %>% left_join(d.games %>% select(gameId, conditionName, condition)) %>% 
  filter(conditionName != "coopCartel") %>% anti_join(rounds_exclude) %>% write_csv(here("data/processed_data/joined_data/filtered_raw_chat.csv"))
```

Clean up a sharable data csv
```{r}
joined_data <- d.raw_chat.final %>% select(-c(index, createdAt, 
                               submitted, conditionName)) %>% 
  # merge chat condition
  left_join(d.games %>% select(gameId, chatEnabled)) %>%
  #merge player selections aligned with chat
  left_join(d.rounds.final %>% 
              select(gameId, playerId,repNum, blockNum, trialNum, 
                     playerResponse, playerEarnings = playerUtility)) %>% 
  #merge player names
  left_join(d.players %>% select(playerId, playerName = name)) %>%
  #merge the raw utility for the selections
  left_join(d.contexts %>% select(gameId, repNum, blockNum, trialNum, 
                                  playerResponse = label, responseRawUtility = utility, blinded)) %>%
  #to avoid confusion, drop any round info thats actually a message
   mutate(playerResponse = ifelse(type == "message", NA, playerResponse),
         playerEarnings = ifelse(type == "message", NA, playerEarnings),
         responseRawUtility = ifelse(type == "message", NA, responseRawUtility),
         blinded = ifelse(type == "message", NA, blinded)) %>%
  select(gameId, condition, chatEnabled,roundID, repNum:trialNum, playerId, 
         playerName, text,  type, playerResponse:responseRawUtility, blinded,everything()) %>% write_csv(here("data/interpretable_transcript.csv"))
```

```{r}
game_completion <- d.rounds %>% 
  group_by(gameId) %>% 
  summarize(num_rounds=max(trialNum+1)) %>% 
  left_join(d.games%>% ungroup() %>% select(gameId, condition, chat=chatEnabled, gameLength)) %>%
  mutate(gameComplete = ifelse(num_rounds == 48, TRUE, FALSE))

#knitr::kable(summary)
message("Full games")
game_completion %>% filter(num_rounds==48)
message("Partial games")
game_completion %>% filter(num_rounds!=48) 
```

@@

```{r, fig.height=3, fig.width=5}
d.by_game_metrics%>% 
  ggplot(aes(x = languageCondition, y = gamePoints, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  ylim(0, 1400)+
  facet_grid(cols = vars(condition)) + labs(x = "Language Condition", y = "Points Earned by Group", title = "Points Earned by Group") + scale_color_bay() + theme_jmank() + theme(legend.position = "none")

>>>>

# Pre-process
Remove joined_data and uncomment the following block to rerun the preprocessing scripts
```{r process-data, message=FALSE, warning=FALSE}
data_list <- c("pilots")
process_all_data(data_list)
join_all_data()
```

@@

```{r}
#exclude BLOCKS with <12 completed (all 3 participants responded) rounds
#exclude trial runs
# exclude 
rounds_exclude <- d.rounds %>% group_by(gameId, blockNum) %>% tally() %>% filter(n!=18) %>% select(gameId,blockNum)

@@

d.raw_chat.final <- d.raw_chat %>% left_join(d.games %>% select(gameId, conditionName, condition)) %>% anti_join(rounds_exclude) %>% write_csv(here("data/processed_data/joined_data/filtered_raw_chat.csv"))
```

Clean up a sharable data csv
```{r}
interpretable_data <- d.raw_chat.final %>% 
  add_chat_info(d.players, d.rounds.final, d.games) %>% 
    left_join(d.contexts %>% select(gameId, repNum, blockNum, trialNum, 
                                  playerResponse = label, 
                                  responseRawUtility = utility, blinded)) %>%
   #to avoid confusion, drop any round info thats actually a message
   mutate(playerResponse = ifelse(type == "message", NA, playerResponse),
         playerUtility = ifelse(type == "message", NA, playerUtility),
         responseRawUtility = ifelse(type == "message", NA, responseRawUtility),
         blinded = ifelse(type == "message", NA, blinded)) %>%
  select(gameId, trialNum, condition, chatEnabled, playerId, name, text, 
         participantAction, type, repNum, 
         blockNum, time, everything(), - submitted, -index, -createdAt) %>% write_csv(here("data/interpretable_transcript.csv"))
```

```{r}
game_completion <- d.rounds %>% 
  group_by(gameId) %>% 
  summarize(num_rounds=max(trialNum+1)) %>% 
  left_join(d.games%>% ungroup() %>% select(gameId, condition, chat=chatEnabled, gameLength)) %>%
  mutate(gameComplete = ifelse(num_rounds == 24, TRUE, FALSE))

#knitr::kable(summary)
message("Full games")
game_completion %>% filter(num_rounds==24)
message("Partial games")
game_completion %>% filter(num_rounds!=24) 
```

@@

```{r, fig.height=3, fig.width=5}
d.by_game_metrics%>% 
  ggplot(aes(x = languageCondition, y = gamePoints, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition)) + labs(x = "Language Condition", y = "Points Earned by Group", title = "Points Earned by Group") + scale_color_bay() + theme_jmank() + theme(legend.position = "none")
